Researchers' perceptions of malaria eradication: findings from a mixed-methodsanalysis of a large online survey

### 2018-04-23 paper.Rmd
format changes

---
title: 'Researchers'' perceptions of malaria eradication: findings from a mixed-methods
  analysis of a large online survey'
csl: elsevier-with-titles.csl
output:
  pdf_document:
    includes:
      in_header: preamble.sty
    keep_tex: yes
    latex_engine: xelatex
  word_document: default
bibliography: library.bib
---

>>>>

---
title: "Researchers' perceptions of malaria eradication: findings from a mixed-methodsanalysis of a large online survey"
csl: journal-of-health-economics.csl
output:
  pdf_document:
    includes:
      in_header: preamble.sty
    keep_tex: yes
    latex_engine: xelatex
  word_document: default
bibliography: library.bib
---
